### 2011-05-26 docs/pubs/EIM-2011/intro.tex

\begin{abstract}
  The Data Manager paper from the last EIM included semantic
  foreshadowing in the 'future directions' section and this is a
  logical continuation of that work. Previously, we saw that the DM
  library enabled data integration tasks provided we knew exactly
  which data attributes from exactly which datasets were "compatible"
  with each other. Here "compatible" means not simply structurally
  similar (e.g. decimal numbers) but also conceptually similar
  (e.g. ocean water temperature in C). By including rich semantic
  annotations we initially show simple integration capabilities where
  the subject domain of our data corpus is relatively constrained
  (i.e. SBC-LTER) and the observational models represented are
  minimally variable (i.e. context excluded). Semantically-enahnced
  query capabilities facilitate this 'smart integration' in multiple
  ways. First, the corpus is refined through compound concept-based
  queries that exercise OBOE-compatible ontological subsumption
  hierarchies to locate roughly equivalent attributes across
  datasets. Additional query constraints are defined in relation to
  the precise observational model formally expressed in OBOE. Finally,
  the actual data values are interrogated so that only those that fall
  in the desired range are returned. From this resultant subset of
  disparate data objects we create a single synthetic data product
  that represents a 'materialization' of the observations. Technical
  discussion will include high-level descriptions of the
  infrastructure and tools employed with focus on our development in
  the rapidly evolving semantic frontier where scalability and best
  practices are particularly germane and equally elusive.
\end{abstract}

>>>>

\section{Introduction}
\label{sec-introduction}
